Gafo-cc-analysis

### 2024-01-19 analysis/gafo-cc-analysis.Rmd
prep merge

```{r}
bm_trial_base <- brm(click ~ targetcentralityx + ageinyears + (targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
                              data   = mdata%>%na.omit(), 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

@@

bm_trial_pred <- brm(click ~ targetcentralityx + ageinyears + touchscreen + older_children + (targetcentralityx|subjid)+ (ageinyears + touchscreen + older_children + targetcentralityx |community),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

@@

pdraws <- draws%>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Sambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Turkey)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "Bayaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)"))

@@

bm_null <- brm(click ~ targetcentralityx + (trialnr + targetcentralityx|subjid),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

bm_cult <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid)+ (1 |community),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

bm_cult_x_age <- brm(click ~ targetcentralityx + ageinyears + (trialnr + targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

```{r}
six_fold_cross_validation <- function(data, m1, m2, m3, repeats) {

  N_ids = n_distinct(data$subjid)
#Prepare results DF
  results <- tibble(m1_score=numeric(), m2_score=numeric() , m3_score=numeric(), m3_beats_m2=logical(), m3_beats_m1=logical(), m2_beats_m1=logical(), m1 = character(), m2 = character(), m3 = character())

@@

  # Split dataset into 6 bins
  bin_data <- data%>%group_by(community) %>% mutate(bin = rep(1:6, length.out = n()))

@@

    # Train models
    up_m1 <- update(m1, newdata=training_data, cores=4,backend = "cmdstanr")
    up_m2 <- update(m2, newdata=training_data, cores=4,backend = "cmdstanr")
    up_m3 <- update(m3, newdata=training_data, cores=4,backend = "cmdstanr")

    # Sample predictions
    preds_m1 <- posterior_predict(up_m1, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
    preds_m2 <- posterior_predict(up_m2, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
    preds_m3 <- posterior_predict(up_m3, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")

    # Evaluate predictive accuracy
  score_m1 <- mean(sqrt(colMeans((testing_data$mean_click - t(preds_m1))**2)))
  score_m2 <- mean(sqrt(colMeans((testing_data$mean_click - t(preds_m2))**2)))
  score_m3 <- mean(sqrt(colMeans((testing_data$mean_click - t(preds_m3))**2)))

  m1_name <-  as.character(substitute(m1))
  m2_name <-  as.character(substitute(m2))
  m3_name <-  as.character(substitute(m3))

    # Record results
    results <- add_row(results,
                       m1_score = score_m1, 
                       m2_score = score_m2, 
                       m3_score = score_m3, 
                       m3_beats_m2 = m3_score < m2_score,
                       m3_beats_m1 = m3_score < m1_score,
                       m2_beats_m1 = m2_score < m1_score, 
                       m1  = m1_name, 
                       m2 = m2_name, 
                       m3 = m3_name)
 }
  }
  return(results)
}
```

@@

```{r}
cv_cult <- six_fold_cross_validation(scdata, bm_base, bm_cult, bm_cult_x_age, 2)
```

## Test for

>>>>

```{r}
bm_trial_base <- brm(click ~ targetcentralityx + ageinyears + (targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
                              data   = mdata%>%na.omit(), 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

@@

bm_trial_pred <- brm(click ~ targetcentralityx + ageinyears + touchscreen + older_children + (targetcentralityx|subjid)+ (ageinyears + touchscreen + older_children + targetcentralityx |community),
                              data   = mdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

@@

pdraws <- draws%>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "akure (nigeria)",
                            leipzig = "leipzig (germany)",
                            `hai||om` = "hai||om (namibia)",
                            khwe = "khwe (namibia)",
                            windhoek = "windhoek (namibia)",
                            stanford = "stanford (usa)",
                            chimfunshi = "chimfunshi (sambia)",
                            mexico = "ocuilan (mexico)",
                            plymouth = "plymouth (uk)",
                            beijing = "beijing (china)", 
                            india = "pune (india)",
                            buenos_aires = "buenos aires (argentina)",
                            auckland = "auckland (new zealand)",
                            turkey = "malatya (turkey)",
                            bandongo = "bandongo (rep. congo)",
                            bayaka = "bayaka (rep. congo)", 
                            uganda = "nyabyeya (uganda)"))

@@

bm_null <- brm(click ~ targetcentralityx + (targetcentralityx|subjid),
                              data   = mdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

bm_age <- brm(click ~ targetcentralityx + ageinyears + (targetcentralityx|subjid),
                              data   = mdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

bm_cult <- brm(click ~ targetcentralityx + (targetcentralityx|subjid)+ (targetcentralityx |community),
                              data   = mdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

bm_cult_age <- brm(click ~ targetcentralityx + ageinyears + (targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
                              data   = mdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 6000, 
                              chains = 4, 
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")
```

```{r}
six_fold_cross_validation <- function(data, m1, m2, m3, m4, repeats) {

  N_ids = n_distinct(data$subjid)
#Prepare results DF
  results <- tibble(
    m1_score=numeric(), 
    m2_score=numeric() , 
    m3_score=numeric(),
    m4_score=numeric(),

    m4_beats_m3=logical(),
    m4_beats_m2=logical(),
    m4_beats_m1=logical(),

    m3_beats_m2=logical(),
    m3_beats_m1=logical(),

    m2_beats_m1=logical(),

    m1 = character(), 
    m2 = character(),
    m3 = character(),
    m4 = character())

@@

  # Split dataset into 6 bins
  bin_data <- data%>%group_by(community)%>%distinct(subjid) %>% mutate(bin = rep(1:6, length.out = n()))

@@

    # Train models
    up_m1 <- update(m1, newdata=training_data, cores=4, threads = threading(8),backend = "cmdstanr")
    up_m2 <- update(m2, newdata=training_data, cores=4, threads = threading(8),backend = "cmdstanr")
    up_m3 <- update(m3, newdata=training_data, cores=4, threads = threading(8),backend = "cmdstanr")
    up_m4 <- update(m4, newdata=training_data, cores=4, threads = threading(8),backend = "cmdstanr")

    # Sample predictions
    preds_m1 <- posterior_predict(up_m1, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
    preds_m2 <- posterior_predict(up_m2, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
    preds_m3 <- posterior_predict(up_m3, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
    preds_m4 <- posterior_predict(up_m4, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")

    # Evaluate predictive accuracy
  score_m1 <- mean(sqrt(colMeans((testing_data$click - t(preds_m1))**2)))
  score_m2 <- mean(sqrt(colMeans((testing_data$click - t(preds_m2))**2)))
  score_m3 <- mean(sqrt(colMeans((testing_data$click - t(preds_m3))**2)))
  score_m4 <- mean(sqrt(colMeans((testing_data$click - t(preds_m4))**2)))

  m1_name <-  as.character(substitute(m1))
  m2_name <-  as.character(substitute(m2))
  m3_name <-  as.character(substitute(m3))
  m4_name <-  as.character(substitute(m4))

    # Record results
    results <- add_row(repeats = i,
                       fold = j, 
                       results,
                       m1_score = score_m1, 
                       m2_score = score_m2, 
                       m3_score = score_m3,
                       m4_score = score_m4,

                       m4_beats_m3 = m4_score < m3_score,
                       m4_beats_m2 = m4_score < m2_score,
                       m4_beats_m1 = m4_score < m1_score,

                       m3_beats_m2 = m3_score < m2_score,
                       m3_beats_m1 = m3_score < m1_score,
                       m2_beats_m1 = m2_score < m1_score,

                       m1  = m1_name, 
                       m2 = m2_name, 
                       m3 = m3_name,
                       m4 = m4_name)
 }
  }
  return(results)
}
```

@@

```{r}
cv_cult <- six_fold_cross_validation(mdata, bm_null, bm_cult, bm_age, bm_cult_age, bm_cult_x_age, 2)
```

```{r}
mean(cv_cult$m4_beats_m1)
```
